\documentclass[a4paper,11pt]{article}

\title{Intelligent Multimedia Systems\\Mean-Shift Object Tracking}
\author{J. v. Turnhout (0312649) \& R. Tobi (0448710)}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{float}
\newcommand{\tbf}{\textbf}
\newcommand{\ds}{\displaystyle}
\newcommand{\ra}{\rightarrow}

%% To complete this course you must pass the exam and hand in a report
%% describing the work you did for this lab. Together with this report
%% you'll hand in your code and some illustrative result videos and still
%% images. Instead of mailing multi-gigabyte video documents, you should
%% put them somewhere in your web site (public_html) and  the link to me.
%%
%% Note that the most important part is to implement the tracker in a correct
%% way. After you made sure your implementation is correct, try the tracker on
%% a video in a different domain (search on the internet to find a good video
%% or create your own video). Keep in mind that when looking for a suitable
%% video, the goal is not to show how good the tracker works, but try to put
%% your finger on the strong and weak parts of the algorithm. After you analyzed
%% these strong and weak points of the algorithm, try to come up with suggestions
%% to improve your design. If there is still enough time, you can implement one
%% or more of your suggestions and analyze the results (for instance, how does
%% your improvement compare to the original algorithm with respect to the weak
%% as well as the strong parts of the original algorithm). If you run out of
%% time, you can describe how you would change the design and explain your
%% expectations of this change. 
%%
%%
%% The report should be about 10 pages long. This should be long enough
%% to give a thorough description of your work, including introduction,
%% conclusions and a discussion. In a paper-style report, the introduction
%% would consist of a problem description (object tracking) and some related
%% work (mention some approaches taken by other researchers, you can use
%% the reader for this or look some up yourself). Then, give an outline
%% of the approach that you have taken (mean-shift and color histograms).
%% Describe the used algorithm and features in you own words. In the next
%% sections, you can write about your implementation and the experimental
%% results. Make sure to mention all relevent issues that you have done
%% and why. For instance, make mention of your approach to color, which
%% color model and why. When writing this part, keep in mind that a reader
%% should be able to reproduce your results by using the information in this
%% report. After that, give a detailed report of the results of your tracker,
%% including graphs and screenshots. In the final section(s), you can give a
%% discussion of your results, in which you can comment on the tracking results
%% and introduce improvements that you have thought of. Furthermore, describe
%% what the effects of your improvement are, or, for lack of time, describe
%% what you expect the effects of the proposed improvements would be. Mention
%% things like processing speed (and possible improvements), the handling of
%% different domains (is one general solution possible, should the tracker be
%% adapted for each domain, how will the adaptation be done, etc.). Don't forget
%% to include your references at the end, and cite your sources in the text.

\begin{document}
	\maketitle

	\abstract{
		We implement a mean-shift tracker for following objects in video.
		Etcetera.
	}

	\section*{Introduction}
		Robust real-time tracking of objects in a sequence of video frames is one of
		the core problems of computer vision. A target object needs to be localized
		and represented in such a way as to be insensitive to changes in illumination,
		rapid movement, occlusion conditions, cluttering, and background appearance.
		Furthermore, the per-frame computations should take no more than $100$
		milliseconds to be useful for real-time applications. These challenging
		conditions have led to many different approaches, most probabilistic in
		nature.
		\\ \\
		KOEN:
		As stated above, tracking means establishing the position of a target
		in subsequent video frames.  So you start with a target at a known
		position, you create a target represenation and then you will try to
		find the position that best matches the target in the next frame.
		The only trick you may use in brute force tracking is exploiting
		the knowledge that the new position of the object will be close
		to the previous one.
		\\ \\
		So you'll probably try to match the target with all position within
		a certain distanceof the previous position and keep the best match.
		This is basically all there is to it (it is after all brute force).
		\\ \\
		The brute-force tracker works by simply comparing all histograms
		of every possible location with the learned target histogram. Since
		this in infeasible for every possible location in the entire image,
		you are allowed to constrain your search space by only looking in a
		region around the previous location. So, if the target at the previous
		frame was at location (x,y), then your search space is restricted from
		(x - width, y - height) to (x + width, y + height), where (width, height)
		determines your search window.
		\\ \\
		The first step towards a Mean-Shift tracker is implementing kernel
		weighted histograms. This means that when you create a histogram of
		your target or candidate, you weigh the pixel values according to
		their distance from the centre. The rationale of this is that
		pixels further from the centre of an object are more likely to
		be occluded or otherwise transformed during the tracking. Another
		reason is that the kernel creates a smooth landscape of histogram
		distances; the smoothness is needed to perform the mean-shift step
		later on. The way I implemented this was by creating a mask of the
		weight function. This was a 2D array, from which I could easily
		retrieve the weight for each pixel position. This weight was added
		to the corresponding bin in the histogram. The mean-shift tracker
		uses the Epanechnikov kernel. The formula is in the paper, but you
		will need these constants: $d = 2, c_d = \pi$. In my implementation
		the kernel is calculated beforehand and store the values in a matrix
		the size of the target region. This way I can look up the weight of
		a pixel with one look in the kernel matrix.
		\\ \\
		For this you need a function that can take the histogram at a certain
		point (x,y coordinates). The nicest way is to use the centre of the
		target as reference (origin), but you can also adjust the coordinates
		to get the same result. By making the mask the same dimensions as the
		target, you can map the locations one-to-one, making it easy to retrieve
		the correct weights.
		\\ \\
		I think it is best that you just start to program and develop by trial
		and error.
		\\ \\
		Since Matlab requires a huge amount of memory for reading all the frames,
		your computer will completely freeze is you try to read all the frames at
		once. Therefore, you should read all the frames incrementally: when you
		need a frame, read it in. So, you can process all the images in a for-loop.
		During the tracking, you may like to save the frames into a movie-file.

	\section*{Theoretical Background}
		Two components can be distinguished in a tracker. The first is concerned
		with localizing and representing the type of object to be tracked up from
		the individual pixels, while the second deals with the high-level task of
		filtering to describe object motion. (FIXME: TOO VAGUE?) In abstract terms,
		this process of filtering can be modelled as a discrete-time dynamical system
		through the well known state-space approach. Each state $x_k$ (for $k=0, 1, ...$)
		characterizes the relevant information about the tracked object, and dynamically
		evolves over time according to $x_k = f_k(x_{k - 1}, v_k)$ where $v_k$ is the
		$k$-th (i.i.d) noise item. The states are not directly observable; rather a
		sequence of measurements $\{z_k\}$ evolving via $z_k = h_k(x_k, n_k)$ (with
		$\{n_k\}$ another i.i.d noise sequence) provides ``hints'' about the true
		state at each time-step $k$, which is a latent variable. The tracker's task
		is now to estimate $x_k$ given all preceding measurements $z_{1:k}$, ie. it
		must recover the unknown probability density function $P(x_k \mid z_{1:k})$.
		This formulation leads to the general technique of recursive Bayesian estimation,
		which assumes the states $\{x_k\}$ and observations $\{z_k\}$ to be the hidden
		and visible parts of a hidden Markov model (HMM). The RBE method constructs the
		p.d.f in two steps conceptually similar to those of the Expectation-Maximization
		algorithm family.
		\\ \\
		%% TODO: mention color-spaces (RGB, nRGB, HSV, OSC), the baseline histogram-based brute-force tracker, ...

	\section*{Implementation}

	\section*{Evaluation and Results}

	\section*{Conclusion}

	\begin{thebibliography}{2}
		\bibitem{KBOT}
			D. Comaniciu, V. Ramesh, P. Meer: \textit{Kernel-Based Object Tracking}
		\bibitem{COLOR}
			T. Gevers: \textit{Color in Image Search Engines}
	\end{thebibliography}

\end{document}
